--- 
title: "title"
format: html
editor: source
execute: 
  echo: false
---

## CFR versus USC

```{r}

library(tidyverse)

df <- bind_rows(
  readr::read_csv("./data/sup_citations.csv")
  , readr::read_csv("./data/enf_citations.csv")
)

df <- df |> 
  mutate(year =  stringr::str_match(doc, "20[0-9]{2}")[ ,1]) 

df |> 
  group_by(source, year, page) |> 
  summarise(
    n = n()
  ) |>  
  filter(!is.na(year)) |> 
  ggplot(aes(year, n, colour = source, group = source)) +
  geom_line(linewidth = 1.05) +
  geom_point(size = 2) +
  facet_wrap(vars(page), scales = "free")

```

#### Unique citations per year. 

There are `r length(unique(df$full))` unique statues cited. 

```{r}

df |> 
  group_by(source, year) |> 
  summarise(
    n = n()
    , n_distinct = n_distinct(full)
  ) |>  
  filter(!is.na(year)) |> 
  ggplot(aes(year, n_distinct, colour = source, group = source)) +
  geom_line(linewidth = 1.05) +
  geom_point(size = 2)

```

# how to compare

how well do lagged supervision citations predict enforcement citations and maybe vice versa just to check

```{r}

df <- df |> 
  mutate(full = stringr::str_replace_all(full, "\n", " ")
         , vol_sec = paste0(volume," ", section)) 
  
  
sup_full <- crossing(
  year = unique(df$year)
  , vol_sec = unique(df$vol_sec)
)

sup_counts <- df |> 
  filter(!is.na(year)) |> 
  filter(!is.na(full)) |> 
  filter(page == "sup") |> 
  group_by(year, vol_sec) |> 
  tally(name = "sup_count")


sup_full <- left_join(sup_full, sup_counts)

sup_full <- sup_full |> 
  mutate(sup_count = ifelse(is.na(sup_count), 0, sup_count)
         , sup_year = year) |> 
  select(-year)

rm(sup_counts)

enf_counts <- df |> 
  filter(!is.na(year)) |> 
  filter(!is.na(full)) |> 
  filter(page == "enf") |> 
  group_by(year, vol_sec) |> 
  tally(name = "enf_count")

final <- left_join(enf_counts, sup_full, by = "vol_sec")

final <- final |> 
  mutate(
    year = as.integer(year)
    , sup_year = as.integer(sup_year)) |> 
  
  filter(sup_year <= year) |> 
  mutate(years_before = year - sup_year) |> 
  mutate(sup_count_scaled = sup_count - mean(sup_count) / sd(sup_count)
         , enf_count_scaled = enf_count - mean(enf_count) / sd(enf_count)
         , year_cnt = max(year) - year 
         , years_before = 1 - (years_before / max(years_before)))

model <- brms::brm(
  
  enf_count ~  (1|vol_sec)
  , data = final
  , family = stats::poisson()
  , chains = 4 
  , cores = 4
  , iter = 2000) 


model_sup.1 <- brms::brm(
  enf_count ~ sup_count_scaled * years_before + (1|vol_sec)
  , data = final
  , family = stats::poisson()
  , chains = 4
  , cores = 4
  , iter = 2000) 


hist(final$years_before)

```




--- 
title: "title"
format: html
editor: source
execute: 
  echo: false
---

## CFR versus USC

```{r}

library(tidyverse)

df <- bind_rows(
  readr::read_csv("./data/sup_citations.csv")
  , readr::read_csv("./data/enf_citations.csv")
)

df <- df |> 
  mutate(year =  stringr::str_match(doc, "20[0-9]{2}")[ ,1]) 

df |> 
  group_by(source, year, page) |> 
  summarise(
    n = n()
  ) |>  
  filter(!is.na(year)) |> 
  ggplot(aes(year, n, colour = source, group = source)) +
  geom_line(linewidth = 1.05) +
  geom_point(size = 2) +
  facet_wrap(vars(page), scales = "free")

```

#### Unique citations per year. 

There are `r length(unique(df$full))` unique statues cited. 

```{r}

df |> 
  group_by(source, year) |> 
  summarise(
    n = n()
    , n_distinct = n_distinct(full)
  ) |>  
  filter(!is.na(year)) |> 
  ggplot(aes(year, n_distinct, colour = source, group = source)) +
  geom_line(linewidth = 1.05) +
  geom_point(size = 2)

```

# how to compare

how well do lagged supervision citations predict enforcement citations and maybe vice versa just to check

```{r}

df <- df |> 
  mutate(full = stringr::str_replace_all(full, "\n", " ")
         , vol_sec = paste0(volume," ", section)) 
  
  
sup_full <- crossing(
  year = unique(df$year)
  , vol_sec = unique(df$vol_sec)
)

sup_counts <- df |> 
  filter(!is.na(year)) |> 
  filter(!is.na(full)) |> 
  filter(page == "sup") |> 
  group_by(year, vol_sec) |> 
  tally(name = "sup_count")


sup_full <- left_join(sup_full, sup_counts)

sup_full <- sup_full |> 
  mutate(sup_count = ifelse(is.na(sup_count), 0, sup_count)
         , sup_year = year) |> 
  select(-year)

rm(sup_counts)

enf_counts <- df |> 
  filter(!is.na(year)) |> 
  filter(!is.na(full)) |> 
  filter(page == "enf") |> 
  group_by(year, vol_sec) |> 
  tally(name = "enf_count")

final <- left_join(enf_counts, sup_full, by = "vol_sec")

final <- final |> 
  mutate(
    year = as.integer(year)
    , sup_year = as.integer(sup_year)) |> 
  
  filter(sup_year <= year) |> 
  mutate(years_before = year - sup_year) |> 
  mutate(sup_count_scaled = sup_count - mean(sup_count) / sd(sup_count)
         , enf_count_scaled = enf_count - mean(enf_count) / sd(enf_count)
         , year_cnt = max(year) - year 
         , years_before = 1 - (years_before / max(years_before)))

model <- brms::brm(
  
  enf_count ~  (1|vol_sec)
  , data = final
  , family = stats::poisson()
  , chains = 4 
  , cores = 4
  , iter = 2000) 


model_sup.1 <- brms::brm(
  enf_count ~ sup_count_scaled * years_before + (1|vol_sec)
  , data = final
  , family = stats::poisson()
  , chains = 4
  , cores = 4
  , iter = 2000) 


hist(final$years_before)

```




